---
title: "User Guide - FARS"
author: "Awal Nazif"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{User Guide - FARS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction to the FARS Package

This package is used to read, summarize and plot maps of data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System.

## How to read a file using the fars_read function in the FARS Package

The fars_read function only takes one argument, the name of csv file to read. If the specified filename exists in the working directory, the fars_read function turns it into a tibble data and if the filename does not exist, "file "filename" does not exists" is printed.

```{r}
fars_read("accident_2013.csv")
```

## How to create a filename based on the input year using the make_filename function

The make_filename function returns a filename in the format "accident_year.csv.bz2", using the year as the input argument.

```{r}
make_filename(2013)
```

## How to read in "FARS" data by specifying the year using the fars_read_years function

The fars_read_years function takes a year as the only argument and returns the months and year as a list. A warning message is thrown, when an invalid year is chosen as an input.

```{r}
fars_read_years(2013)
```

## How to summarize number per month in a specified year using the fars_summarize_years function

This fars_summarize_years function summarizes "FARS" data per month in a given year, tha is specifid as the input argument. 

```{r}
fars_summarize_years(2013)
```

## How to create a map of a givne state with the distribution of accidents

The fars_map_state function takes two argument, the state number (state.num) and the year and plots the geographical boundaries of a state and the distribution of reported accidents within the state.

```{r}
fars_map_state(18, 2013)
```


